NeuronUnit: Validation Tests for Neurophysiology

### 2013-11-02 NeurounitFrontiers/Paper.tex
Wrapped with Frontiers template

\documentclass[11pt,letterpaper]{article}
\pagestyle{plain}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{python_syntax}
\usepackage[sort&compress]{natbib}
\usepackage{bibentry}
\usepackage{todonotes}
\usepackage{url}
\usepackage[compact]{titlesec}
\titleformat{\subsection}[runin]
{\normalfont\large\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[runin]
{\normalfont\large\bfseries}{\thesubsubsection}{1em}{}
\usepackage{enumitem}
\usepackage[
top    = 1in,
bottom = 1in,
left   = 1in,
right  = 1in]{geometry}
\usepackage{caption}
\captionsetup{belowskip=0pt,aboveskip=0pt}
\linespread{0.92} % NSF allows up to 6 lines per inch.  
\def\UrlFont{\em} % Italicize all URLs.  
\frenchspacing
\setlist{nolistsep} % or \setlist{noitemsep} to leave space around whole list
\lstset{
	basicstyle=\small\ttfamily,
	breaklines=true,
	language=Python,
	}
\let\verbx\lstinline
\newcommand{\bfhead}[1]{\noindent \textbf{#1:}}

@@

\section{Abstract}
Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
However, model validation remains an informal and incomplete process, especially in fields like neuroscience where the available data is growing rapidly.   
This has made it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.

Software engineers validate software by developing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. Suites of such unit tests that collectively capture the desired program behavior provide evidence for its validity and correctness. Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
executable functions, here written in Python, that compare model predictions against single empirical observations to  produce a score indicating agreement between the model and the data. Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
Building on this framework, we develop \textit{NeuronUnit}, a library that supports validation testing for neurophysiology.

@@

Today, scientists contribute a new model to the research community by submitting a paper describing how the model works, along with selected figures demonstrating its scope and validity and comparing its validity to other models with the same scope. 
Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, drawing on their knowledge of prior publications. 
Unfortunately, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists\cite{jinha_article_2010}.

@@

Professional software developers face similar issues. 
They must understand the scope of each component of a software project and validate it by measuring how well each component achieves its stated goals. 
But software developers do not validate components by simply choosing a few interesting inputs and presenting the outputs to reviewers. 
Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively specify the scope of each component and validate the functionality of its implementation as it is being developed and modified. 
Each test individually checks that a small portion of the program meets a single correctness criterion. For example, a unit test might verify that one function within the program correctly handles malformed inputs. 
Collectively, the test results serve as a summary of the validity of the project as it progresses through its development cycle. 
Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
This methodology is widely adopted in practice\cite{beck2003}.

@@

Test-driven methodologies have started to see success in science as well. 
Modeling competitions in neuroscience, for example, are typically organized around a collection of simple validation criteria, implemented as executable tests. 
These competitions continue to drive important advances and improve scientists' understanding of the relative merits of different models. 
For example, the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
the ``Hopfield'' challenge\cite{hopfield_what_2000} tested techniques for generating neuronal network form given its function; 
the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity\cite{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction\cite{diadem_url}; and 
examples from other subfields of biology abound\cite{dream_url}.
% \begin{figure}%{r}{0.6\textwidth}
% %\vspace{-38px}
% \includegraphics[scale=0.75]{sciunit_overview.pdf}
% \caption{Proposal overview. 
% \small{i) The \textit{SciUnit} framework can generate discipline-specific libraries for tests generation and model interfacing.  
% \textit{NeuronUnit} is proposed and described here.  Experimental data guides test development; model generation informs and is informed by these \textit{SciUnit} libraries.  
% Each \text{SciUnit} test suite repository on GitHub is indexed by the \textit{SciDash} web application.  
% Test suites for OSB and QSNMC (described in the text) are being built. 
% \textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
% %\vspace{-10px}
% \label{fig:sciunit_overview}
% \end{figure}
% \leavevmode
% \vspace{-0px}
\begin{figure}
\vspace{-38px}
\centering
\includegraphics[scale=0.6]{diagram1.pdf}
\vspace{-55px}
\caption{NeuronUnit overview. NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework. NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project \cite{osb_url}, and single neuron electrophysiology data available as part of the NeuroElectro Project \cite{neuroelectro_url}.  Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}  
\label{fig:sciunit_overview}
\end{figure}
\leavevmode
\vspace{-0px}

Each of these examples has leveraged \emph{ad hoc} infrastructure to support test generation. 
While the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that could be implemented once. 
Recognizing this, we have developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit}\cite{sciunit_url}. 
To demonstrate the power of this framework and show how it can be used to bridge several existing neuroinformatics tools, we then developed \textit{NeuronUnit\-}. 
This library allows scientists to build \textit{SciUnit} tests that validate \text{NeuroML} models against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.  This is summarized in Figure \ref{fig:sciunit_overview}, which shows the relationships between the layers described here.
% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.

@@

  def run_test(self, model):
    inputs, means, stds = self.inputs, self.means, self.stds
    n = len(inputs)
    counts = numpy.empty((n,))
    for i in xrange(n):
      counts[i] = model.spike_count_from_current(inputs[i])
    chisquared = sum((counts-means)**2 / means) # An array of chi-squared values.  
    p = scipy.stats.chi2.cdf(chisquared,n-1) # An array of p-values.  
    pooled_p = sciunit.utils.fisherp(p_array) # A pooled p-value.  
    return sciunit.PValue(pooled_p, related_data={
      "inputs": inputs, "counts": counts, "obs_means": means, "obs_stds": stds
    })
\end{python}
\vspace{-5px}
\caption{A single neuron spike count test family implemented using \textit{SciUnit}. This family contains logic common to many different systems, so it is distributed in the \textit{NeuronUnit} repository (see Sec. \ref{sec:neuronunit}).}
\label{fig:rate_test}
\vspace{-15px}
\end{figure}

%Simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.  
We begin by constructing an example validation test suite. 
Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons in some brain region, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.  
A model claiming to capture this cell type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.

@@

Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{run_test} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
To specify the interface between the test and the model (that is, to specify an appropriate scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig. \ref{fig:rate_test}. 
Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java \cite{java_interfaces_url}. 
In Python, they are written as classes with unimplemented members. 
The capability required by the test in Fig. \ref{fig:rate_test} is shown in Fig. \ref{fig:capability}. 
In \textit{SciUnit}, classes defining capabilities are tagged as such by inheriting from \verbx{sciunit.Capability}. The test in Figure \ref{fig:rate_test} uses this capability on line 19 to produce a spike count prediction for each input current.

The remainder of the \verbx{run_test} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.PValue}, a subclass of \verbx{sciunit.Score} included with \textit{SciUnit}. In addition to the score itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for  those who may wish to examine the result in more detail. 
In this case we save the input currents, the model outputs and the observed means and standard deviations alongside the score (line 24). 
%We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.

@@

A simple \emph{family} of models, \verbx{LinearModel}, implementing the capability in Fig. \ref{fig:capability} as well as another capability shown in Fig. \ref{fig:training}, is shown in Fig. \ref{fig:simple_model}. 
Models in this family, \verbx{LinearModel}, produce a spike count by applying a linear transformation to the mean of the provided input current. 
The family is parameterized by a scale factor and offset, both scalars. 
To create a \emph{particular} model, the modeler may choose particular parameter values, just as with test families:
\begin{python}
CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
\end{python}
Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
An alternative test design to the one in Fig. \ref{fig:rate_test} would add a second required capability (Fig. \ref{fig:training}) and a corresponding training phase to the \verb|run_test| method. 
This design would be relevant only for those models for which parameters can be adjusted without human involvement. 
Whether to build a training phase into the test protocol is a choice left to each modeler. 
Although Fig. \ref{fig:rate_test} does not include a training phase, if training data is available then models that nevertheless implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
\begin{python}
CA1_linear_model_fit = LinearModel()
CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
\end{python}
\begin{figure}
\begin{python}
class LinearModel(sciunit.Model, SpikeCountFromCurrent, 
    TrainSpikeCountFromCurrent):
  def __init__(self, scale=None, offset=None): 
    self.scale, self.offset = scale, offset

@@

\begin{figure}
\begin{python}
# Interface with neuroelectro.org to search for spike widths of CA1 Pyramidal cells. 
reference_data = NeuroElectroSummary(neuron={'id':85}, ephysprop={'id':23})
reference_data.get_values()  # Get summary data for the above. 
model = CA1PyramidalCellModel(population_name="CG_CML_0") # Initialize the model with some parameters.
test = SpikeWidthTestDynamic( # Initialize the test.    
	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics from the reference data
	model_args = {'current':40.0}, # Somatic current injection in pA.  
	comparator = ZComparator), # A comparison class that implements a Z-score.  
result = sciunit.judge(test,model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
result.summarize() # Summarize the result.  
\end{python}
\caption{Working example of a testing in \textit{NeuronUnit}}
\label{fig:neuronunit_example}
\vspace{-15px}
\end{figure}

@@

\section{Acknowledgements}
We thank Sharon Crook, Jonathan Aldrich, Shreejoy Tripathy, and Padraig Gleeson for their support of this project.  
The work was supported in part by grant R01MH081905 from the National Institute of Mental Health. 
The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.

\bibliographystyle{unsrt}
\bibliography{references,references_crook,urls,references_ja}
%\listoftodos
\end{document}

>>>>

\documentclass{frontiersSCNS}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{times}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{python_syntax}
\usepackage{bibentry}
\usepackage{todonotes}
\usepackage{url}
\usepackage{lineno}
\usepackage{caption}
\usepackage[english]{babel} 
\def\UrlFont{\em} % Italicize all URLs.  
\lstset{
	basicstyle=\small\ttfamily,
	breaklines=true,
	language=Python,
	}
\let\verbx\lstinline
\newcommand{\bfhead}[1]{\noindent \textbf{#1:}}

\linenumbers
\copyrightyear{}
\pubyear{}

\def\journal{NeuroInformatics}%%% write here for which journal %%%
\def\DOI{}
\def\articleType{Methods}
\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{Richard C. Gerkin\,$^{1,*}$, Cyrus Omar\,$^{2}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$School of Life Sciences, Arizona State University, Tempe, AZ, USA \\
$^{2}$Dept. of Computer Science, Carnegie Mellon University, Pittsburgh, PA, USA  }
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Rick Gerkin}
\def\corrAddress{ISTB-1 476}
\def\corrEmail{rgerkin@asu.edu}

% \color{FrontiersColor} Is the color used in the Journal name, in the title, and the names of the sections.

@@

\onecolumn
\firstpage{1}

\title[Running Title]{NeuronUnit: Validation Tests for Neurophysiology}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\topic{}% If your article is part of a Research Topic, please indicate here which.

\maketitle

\begin{abstract}
Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
However, model validation remains an informal and incomplete process, especially in fields like neuroscience where the available data is growing rapidly.   
This has made it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.

Software engineers validate software by developing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. 
Suites of such unit tests that collectively capture the desired program behavior provide evidence for its validity and correctness. 
Drawing inspiration from this practice, we developed the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
executable functions, here written in Python, that compare model predictions against single empirical observations to produce a score indicating agreement between the model and the data. 
Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
Building on this framework, we describe here \textit{NeuronUnit}, a library that supports validation testing for neurophysiology.

\tiny
 \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

@@

Today, scientists contribute a new model to the research community by submitting a paper describing how the model works, along with selected figures demonstrating its scope and validity and comparing its validity to other models with the same scope. 
Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, drawing on their knowledge of prior publications. 
However, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists\cite{jinha_article_2010}.

@@

Professional software developers face similar issues. 
They must understand the scope of each component of a software project and validate it by measuring how well each component achieves its stated goals. 
But software developers do not validate components by simply choosing a few interesting inputs and presenting the outputs to reviewers. 
Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively specify the scope of each component and validate the functionality of its implementation as it is being developed and modified\cite{beck2003}. 
Each test individually checks that a small portion of the program meets a single correctness criterion. For example, a unit test might verify that one function within the program correctly handles malformed inputs. 
Collectively, the test results serve as a summary of the validity of the project as it progresses through its development cycle. 
Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
This methodology is widely adopted in practice\cite{beck2003}.

@@

Test-driven methodologies have started to see success in neuroscience as well. 
Modeling competitions in neuroscience, for example, are typically organized around a collection of simple validation criteria, implemented as executable tests. 
These competitions continue to drive important advances and improve scientists' understanding of the relative merits of different models. 
For example, the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
the ``Hopfield'' challenge\cite{hopfield_what_2000} tested techniques for generating neuronal network form given its function; 
the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity\cite{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction\cite{diadem_url}; and 
examples from other subfields of biology abound\cite{dream_url}.
% \begin{figure}%{r}{0.6\textwidth}
% %\vspace{-38px}
% \includegraphics[scale=0.75]{sciunit_overview.pdf}
% \caption{Proposal overview. 
% \small{i) The \textit{SciUnit} framework can generate discipline-specific libraries for tests generation and model interfacing.  
% \textit{NeuronUnit} is proposed and described here.  Experimental data guides test development; model generation informs and is informed by these \textit{SciUnit} libraries.  
% Each \text{SciUnit} test suite repository on GitHub is indexed by the \textit{SciDash} web application.  
% Test suites for OSB and QSNMC (described in the text) are being built. 
% \textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
% %\vspace{-10px}
% \label{fig:sciunit_overview}
% \end{figure}
% \leavevmode
% \vspace{-0px}
\begin{figure}
\vspace{-38px}
\centering
\includegraphics[scale=0.6]{diagram1.pdf}
\vspace{-55px}
\caption{NeuronUnit overview. NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework. NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project\cite{osb_url}, and single neuron electrophysiology data available as part of the NeuroElectro Project\cite{neuroelectro_url}.  Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}  
\label{fig:sciunit_overview}
\end{figure}
\leavevmode
\vspace{-0px}

Each of these examples has leveraged \emph{ad hoc} infrastructure to support test generation. 
While the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that could be implemented once. 
Recognizing this, we developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit}\cite{sciunit_url}. 
Here we describe \textit{NeuronUnit\-}, which builds upon \textit{SciUnit}, allowing neuroscientists to build \textit{SciUnit} tests that validate neurophysiology models against electrophysiological data.  We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the Open Source Brain project\cite{osb_url} can be test in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project}\cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.  This is summarized in Figure \ref{fig:sciunit_overview}, which shows the relationships between the layers described here.
% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.

@@

  def _judge(self, model):
    inputs, means, stds = self.inputs, self.means, self.stds
    n = len(inputs)
    counts = numpy.empty((n,))
    for i in xrange(n):
      counts[i] = model.spike_count_from_current(inputs[i])
    chisquared = sum((counts-means)**2 / means) # An array of chi-squared values.  
    p = scipy.stats.chi2.cdf(chisquared,n-1) # An array of p-values.  
    pooled_p = sciunit.utils.fisherp(p_array) # A pooled p-value.  
    return sciunit.PValue(pooled_p, related_data={
      "inputs": inputs, "counts": counts, "obs_means": means, "obs_stds": stds
    })
\end{python}
\vspace{-5px}
\caption{An example single neuron spike count test class implemented using \textit{SciUnit}. Because this implementation contains logic common to many different systems, \textit{NeuronUnit} was developed to provide a simpler means to deliver it (see Sec. \ref{sec:neuronunit}).}
\label{fig:rate_test}
\vspace{-15px}
\end{figure}

%Simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.  
We first illustrate the form of a generic example \textit{SciUnit} test suite that could be used in neurophysiology. 
Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons in some brain region, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.  
A model claiming to capture this cell type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.

@@

Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{_judge} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
To specify the interface between the test and the model (that is, to specify an appropriate scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig. \ref{fig:rate_test}. 
Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java \cite{java_interfaces_url}. 
In Python, they are written as classes with unimplemented members. 
The capability required by the test in Fig. \ref{fig:rate_test} is shown in Fig. \ref{fig:capability}. 
In \textit{SciUnit}, classes defining capabilities are tagged as such by inheriting from \verbx{sciunit.Capability}. The test in Figure \ref{fig:rate_test} uses this capability on line 19 to produce a spike count prediction for each input current.

The remainder of the \verbx{run_test} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.PValue}, a subclass of \verbx{sciunit.Score} included with \textit{SciUnit}. In addition to the score itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for  those who may wish to examine the result in more detail. 
In this case we save the input currents, the model outputs and the observed means and standard deviations alongside the score (line 24). A \verbx{sciunit.judge} function executes the test's \verbx{_judge} method on the model, and then on the returned \verbx{sciunit.Score} object sets attributes referring to the model and test instances themselves, producing a complete record of the test result (Fig. \ref{fig:neuronunit_example}).    
%We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.

@@

A simple \emph{family} of models, \verbx{LinearModel}, implementing the capability in Fig. \ref{fig:capability} as well as another capability shown in Fig. \ref{fig:training}, is shown in Fig. \ref{fig:simple_model}. 
Models in this family, \verbx{LinearModel}, produce a spike count by applying a linear transformation to the mean of the provided input current. 
The family is parameterized by a scale factor and offset, both scalars. 
To create a \emph{particular} model, the modeler may choose particular parameter values, just as with test families:
\begin{python}
CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
\end{python}
Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
An alternative test design to the one in Fig. \ref{fig:rate_test} would add a second required capability (Fig. \ref{fig:training}) and a corresponding training phase to the \verbx{_judge} method. 
This design would be relevant only for those models for which parameters can be adjusted without human involvement. 
Whether to build a training phase into the test protocol is a choice left to each modeler. 
Although Fig. \ref{fig:rate_test} does not include a training phase, if training data is available then models that nevertheless implement a training capability (like \verbx{LinearModel}) can simply be trained explicitly by calling the capability method just like any other Python method:
\begin{python}
CA1_linear_model_fit = LinearModel()
CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
\end{python}
\begin{figure}
\begin{python}
class LinearModel(sciunit.Model, SpikeCountFromCurrent, 
    TrainSpikeCountFromCurrent):
  def __init__(self, scale=None, offset=None): 
    self.scale, self.offset = scale, offset

@@

\begin{figure}
\begin{python}
# Interface with neuroelectro.org to search for spike widths of CA1 Pyramidal cells. 
reference_data = NeuroElectroSummary(neuron={'id':85}, ephysprop={'id':23})
reference_data.get_values()  # Get summary data for the above. 
model = CA1PyramidalCellModel(population_name="CG_CML_0") # Initialize the model with some parameters.
test = SpikeWidthTestDynamic( # Initialize the test.    
	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics from the reference data
	model_args = {'current':40.0}, # Somatic current injection in pA.  
	comparator = ZComparator), # A comparison class that implements a Z-score.  
result = sciunit.judge(test,model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
result.summarize() # Summarize the result.  
\end{python}
\caption{Working example of testing in \textit{NeuronUnit}}
\label{fig:neuronunit_example}
\vspace{-15px}
\end{figure}

@@

\section*{Disclosure/Conflict-of-Interest Statement}
%All relationships financial, commercial or otherwise that might be perceived by the academic community as representing a potential conflict of interest must be described. If no such relationship exists, authors will be asked to declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section*{Acknowledgements}
We thank Sharon Crook, Jonathan Aldrich, Shreejoy Tripathy, and Padraig Gleeson for their support of this project.  
The work was supported in part by grant R01MH081905 from the National Institute of Mental Health. 
The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.

%\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
\bibliographystyle{frontiersinSCNS&ENG} % for Medicine articles
\bibliography{references,references_crook,urls,references_ja}

%\bibliographystyle{unsrt}
%\bibliography{references,references_crook,urls,references_ja}
%\listoftodos
\end{document}
